WI FastPlants: Heritability of number of cotelydons

### 2020-07-29 cotyledon-data-analysis.Rmd
fixed typo

```{r}
dat2 = data.frame(generation=dat$Generation)
dat2$cots = "dycot"
dat2$cots[dat$Cotyledons > 2] = "polycot"
dat2 = within(dat2, cots<-factor(cots))
summary(dat2)
write.table(dat2,file="data/polycot-data-2020-categories.csv", row.names = FALSE, sep=",")

>>>>

```{r}
dat2 = data.frame(generation=dat$Generation)
dat2$cots = "dicot"
dat2$cots[dat$Cotyledons > 2] = "polycot"
dat2 = within(dat2, cots<-factor(cots))
summary(dat2)
write.table(dat2,file="data/polycot-data-2020-categories.csv", row.names = FALSE, sep=",")
